---
# Reproducible Research: Peer Assessment 1
## [Rafael Reséndiz Ramírez] (https://github.com/Rafael-Resendiz)
### [PA1_template.Rmd] (https://github.com/Rafael-Resendiz/RepData_PeerAssessment1/edit/master/PA1_template.Rmd)

---


## Loading and preprocessing the data
Show any code that is needed to

Load the data (i.e. read.csv())

Process/transform the data (if necessary) into a format suitable for your analysis  
```{r readdata}
     fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip?accessType=DOWNLOAD"  
     download.file(fileUrl, destfile = "/Users/administrador/Specialization/Activity_monitoring_data.zip", 
     method = "curl")    
````
unzip the file    
```{r readdata}
     unzip("Activity_monitoring_data.zip")  
````
Read the file   
```{r readdata}
     activity <- read.table("../Specialization/activity.csv", sep = ",", header = TRUE)    
```
Show the head file
```{r readdata}
     head(activity)    
````
Stream the databases
```{r readdata}
     str(activity)   
```
         

## What is mean total number of steps taken per day?

The *xtabs* and *mean* function can be used to determine the mean total number of steps taken per day

```{r readdata}
     totalNumberSteps <- xtabs(steps ~ date,activity)

     mean(totalNumberSteps)  
```

Other way
Just to check the total number of steps per day are being calculated correctly, we sum the steps for days explicitly
 and dividing that number by the total number of days.
 ```{r readdata}
      sum(activity$steps, na.rm=TRUE)/length(levels(activity$date)) 
```
         
 
 
 


## What is the average daily activity pattern?

```{r readdata}
     str(activity)   
```
         



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
